\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-09 doc/sw-cfhtls.tex
Appendices done. #203

The {\bf bottom-left panels of \Fref{fig:detmis} show the} missed or rejected lenses. The green (and red)
trajectories show visually easier (and more difficult) to identify
lenses. In spite of some mild qualitative differences, both set of
trajectories have very similar behaviour. The trajectories in panel e
are typical of this sample in terms of Nclass and the dominance of short
negative kicks. Panel f represents a small fraction of this sample
where the kicks are only short and negative. The panel g shows how some
lenses receive a bunch of large positive kicks which are led to
rejection by still mostly negative short kicks. Finally, panel h shows
those cases of lenses which received almost sufficient number of large
positive kicks to be detected but ended up being rejected.

The {\bf top-left panels of \Fref{fig:detmis}} show the detected lenses. The cases shown with green trajectories
in each panel can be thought of counterparts of the trajectories of the
missed lenses in the corresponding bottom panels except that the type of
volunteers are different. Most detected lenses are similar to the case
in panel a that are detected within a few classifications coming from
large positive kicks.  Panel b represents a few odd cases which are
dominated mainly by short positive kicks. Panel c shows a lens getting
more classifications but do not reach the detection or rejection
thresholds because of the tug between positive and negative kicks mostly
from experienced volunteers.  Panel d represents the extreme cases when
the images are on the verge of being rejected but are saved thanks to a
series of large positive kicks.  The red trajectories are some more
examples of randomly selected cases which demonstrate how having
sufficient number of large positive kicks allows lenses to be detected
in spite of several short negative kicks.

@@

As described in the appendix of \PaperOne, the posterior probability $P$
of a subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the
volunteers who clicked on the subject, via Bayes' Theorem. Each agent
will apply a ``kick'' of a different size to the subject probability,
$\Delta\log{P}$, which can be either positive (if the classifier thinks
the subject contains a lens) or negative (if the classifier thinks the
subject does not contain a lens). For instance, given a subject
(not) containing a lens, a volunteer with high ($P_{\rm D}$) $P_{\rm L}$
implies a large (negative) positive kick irrespective the value of
($P_{\rm L}$) $P_{\rm D}$ as shown in the (right most) middle panel of
\Fref{fig:skilldlnp}. However, large (negative) positive kicks are
still possible for a volunteer located in the (lower) upper triangle
with different combinations of ($P_{\rm L}$, $P_{\rm D}$) suggesting that
the kick is not a simple function of ($P_{\rm L}$, $P_{\rm D}$).

>>>>

The {\bf bottom-left panels of \Fref{fig:detmis} show the} missed or rejected lenses. The green (and red)
trajectories show visually easier (and more difficult) to identify
lenses. In spite of some mild qualitative differences, both set of
trajectories have very similar behaviour. The trajectories in panel (e)
are typical of this sample in terms of Nclass and the dominance of short
negative kicks. Panel (f) represents a small fraction of this sample
where the kicks are only short and negative. The panel (g) shows how some
lenses receive a bunch of large positive kicks which are led to
rejection by still mostly negative short kicks. Finally, panel (h) shows
those cases of lenses which received almost sufficient number of large
positive kicks to be detected but ended up being rejected.

The {\bf top-left panels of \Fref{fig:detmis}} show the detected lenses.
The cases shown with green trajectories
in each panel can be thought of counterparts of the trajectories of the
missed lenses in the corresponding bottom panels except that the type of
volunteers are different. Most detected lenses are similar to the case
in panel (a) that are detected within a few classifications coming from
large positive kicks.  Panel (b) represents a few odd cases which are
dominated mainly by small positive kicks. Panel (c) shows a lens getting
more classifications, but not reaching the detection or rejection
thresholds because of the tug between positive and negative kicks mostly
from experienced volunteers.  Panel (d) represents two extreme cases when
the images are on the verge of being rejected but are saved thanks to a
series of large positive kicks.  The red trajectories are some more
examples of randomly selected cases which demonstrate how having
sufficient number of large positive kicks allows lenses to be detected
in spite of several short negative kicks.

@@

As described in the appendix of \PaperOne, the posterior probability $P$
of a subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the
volunteers who clicked on the subject, via Bayes' Theorem. Each agent
will apply a ``kick'' of a different size to the subject probability,
$\Delta\log{P}$, which can be either positive (if the classifier thinks
the subject contains a lens) or negative (if the classifier thinks the
subject does not contain a lens). For instance, given a subject
containing a lens, a volunteer with high $P_{\rm L}$
implies a large (negative) positive kick irrespective of the value of
$P_{\rm D}$, as shown in the middle panel of
\Fref{fig:skilldlnp}. However, large (negative) positive kicks are
still possible for a volunteer located in the (lower) upper triangle
with different combinations of ($P_{\rm L}$, $P_{\rm D}$) suggesting that
the kick is not a simple function of ($P_{\rm L}$, $P_{\rm D}$).
